**The status of the microbial census: an update**

### 2015-11-19 results/tables/build_table_1.Rmd
Fix sanitizing of text
Generate output text file

```{r table1, results='asis', echo=FALSE, warning=FALSE, eval=TRUE}
require(xtable, quietly=TRUE)

@@

fine <- c("", "Brackish", "Brackish sediment", "Freshwater", "Freshwater sediment", "Hydrothermal vent", "Ice", "Marine", "Marine sediment", "Other", "Digesters", "Food-associated", "Industrial/mining", "Pollution associated", "Other", "Root", "Surface", "Other", "Agriculture", "Desert", "Permafrost", "Other", "Arthropod", "Other invertebrate", "Vertebrate", "Other", "", "", "")

abbreviation <- c("AE", "AQB", "AQBS", "AQF", "AQFS", "AQH", "AQI", "AQM", "AQMS", "AQO", "BD", "BF", "BI", "BP", "BO", "PR", "PS", "PO", "SA", "SD", "SP", "SO", "ZA", "ZN", "ZV", "ZO", "OT")

@@

#abbreviation <- c(abbreviation, "", "")
composite <- cbind(coarse, fine, bact_count, bact_sobs, bact_good_coverage, bact_schloss_coverage, arch_count, arch_sobs, arch_good_coverage, arch_schloss_coverage)
composite <- rbind(c("", "", "\\bigcell{c}{Sequences \\\\ (N)}", "\\bigcell{c}{OTUs \\\\ (N)}", "\\bigcell{c}{\\% Seq. \\\\ Coverage}", "\\bigcell{c}{\\% OTU \\\\ Coverage}", "\\bigcell{c}{Sequences \\\\ (N)}", "\\bigcell{c}{OTUs \\\\ (N)}", "\\bigcell{c}{\\% Seq. \\\\ Coverage}", "\\bigcell{c}{\\% OTU \\\\ Coverage}"), composite)

@@

addtorow <- list(pos=list(0, 1),
				command=c('\\multirow{4}{*}{Coarse} & \\multirow{4}{*}{Fine} & \\multicolumn{4}{c}{Bacterial} & \\multicolumn{4}{c}{Archaeal} \\\\ \\cmidrule(r){3-6}	\\cmidrule(r){7-10}', '\\hline '))

>>>>

```{r table1, results='asis', echo=FALSE, warning=FALSE, eval=TRUE}
require(xtable, quietly=TRUE)
options(xtable.sanitize.text.function=identity)

@@

fine <- c("", "Brackish", "Brackish sediment", "Freshwater", "Freshwater sediment", "Marine", "Marine sediment", "Hydrothermal vent", "Ice", "Other", "Digesters", "Food-associated", "Industrial/mining", "Pollution associated", "Other", "Root", "Surface", "Other", "Agriculture", "Desert", "Permafrost", "Other", "Vertebrate", "Arthropod", "Other invertebrate", "Other", "", "", "")

abbreviation <- c("AE", "AQB", "AQBS", "AQF", "AQFS", "AQM", "AQMS", "AQH", "AQI", "AQO", "BD", "BF", "BI", "BP", "BO", "PR", "PS", "PO", "SA", "SD", "SP", "SO", "ZV", "ZA", "ZN",  "ZO", "OT")

@@

#abbreviation <- c(abbreviation, "", "")

composite <- cbind(coarse, fine, bact_count, bact_sobs, bact_good_coverage, bact_schloss_coverage, arch_count, arch_sobs, arch_good_coverage, arch_schloss_coverage)
write.table(composite, file=paste0(PROJHOME, "/data/process/table1_data.tsv"))

composite <- rbind(c("", "", "\\bigcell{c}{Sequences \\\\ (N)}", "\\bigcell{c}{OTUs \\\\ (N)}", "\\bigcell{c}{\\% Seq. \\\\ Coverage}", "\\bigcell{c}{\\% OTU \\\\ Coverage}", "\\bigcell{c}{Sequences \\\\ (N)}", "\\bigcell{c}{OTUs \\\\ (N)}", "\\bigcell{c}{\\% Seq. \\\\ Coverage}", "\\bigcell{c}{\\% OTU \\\\ Coverage}"), composite)

@@

addtorow <- list(pos=list(0, 1),
				command=c('\\multirow{4}{*}{Coarse} & \\multirow{4}{*}{Fine} & \\multicolumn{4}{c}{Bacteria} & \\multicolumn{4}{c}{Archaea} \\\\ \\cmidrule(r){3-6}	\\cmidrule(r){7-10}', '\\hline '))
